|

### 2024-01-28 rmds/figures-supp.Rmd
changes

## Figures
```{r, fig.width = 12, fig.height = 10}
ggplot(data %>% filter(par_name %in% "m50")) +
  geom_point(aes(as.factor(Nsamples), conv_success, col = repro_freq, group = repro_freq)) + 
  geom_line(aes(as.factor(Nsamples), conv_success, col = repro_freq, group = repro_freq)) +
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) +
  scale_color_brewer(palette = "Spectral") + 
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Number of samples", y = "Convergence success (%)", title = "Model convergence") +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```
Figure S1.

```{r, fig.width = 12, fig.height = 10}
ggplot(data %>% filter(par_name %in% "m50")) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), rel_error, col = repro_freq, group = repro_freq)) +
  geom_line(aes(as.factor(Nsamples), rel_error, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  scale_color_brewer(palette = "Spectral") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) + 
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "Mean % relative error", title = "Bias - Length at 50% maternity") +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")

```
Figure S2.

@@

```
Figure S3. Note 2PLF-maturity and 3PLF-fixed methods are identical

```{r, fig.width = 12, fig.height = 10}
ggplot(data %>% filter(par_name %in% "m50")) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), abs_error, col = repro_freq, group = repro_freq)) +
  geom_line(aes(as.factor(Nsamples), abs_error, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  scale_color_brewer(palette = "Spectral") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) + 
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "Mean % absolute relative error", title = "Precision - Length at 50% maternity") +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```
Figure S4.

```{r, fig.width = 12, fig.height = 10}
ggplot(data %>% filter(par_name %in% "c")) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), abs_error, col = repro_freq, group = repro_freq)) +
  geom_line(aes(as.factor(Nsamples), abs_error, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  scale_color_brewer(palette = "Spectral") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) + 
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "Mean % absolute relative error", title = expression("Precision - "~italic(P)[Max])) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```
Figure S5.
\newpage

```{r fig.width = 12, fig.height=7}
ggplot(data %>% filter(par_name %in% "m50", method_long %in% c("3PLF - estimated", "3PLF - fixed"))) +
  geom_hline(yintercept = 50, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), int_coverage, col = repro_freq, group = repro_freq)) +
  geom_line(aes(as.factor(Nsamples), int_coverage, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  scale_color_brewer(palette = "Spectral") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) + 
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "% interval coverage", title = "Interval coverage - Length at 50% maternity") +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```
Figure S6.
\newpage

```{r fig.width = 12, fig.height=5}
ggplot(data %>% filter(par_name %in% "c", method_long %in% c("3PLF - estimated"))) +
  geom_hline(yintercept = 50, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), int_coverage, col = repro_freq, group = repro_freq)) +
  geom_line(aes(as.factor(Nsamples), int_coverage, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  scale_color_brewer(palette = "Spectral") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) + 
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "% interval coverage", title = expression("Interval coverage - "~italic(P)[Max])) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```
Figure S7. 
\newpage

```{r, fig.width = 11, fig.height = 8.5}
filter(data, method_long %in% c("3PLF - estimated", par_name %in% "c")) %>% 
  ggplot() + 
  geom_tile(aes(x = as.factor(Nsamples_sel), y = repro_freq, fill = n_maternal)) + 
  geom_text(aes(x = as.factor(Nsamples_sel), y = repro_freq, label = round(n_maternal, 0))) +
  scale_fill_viridis_c(trans = "log10") + 
  guides(fill = guide_colorbar(title = bquote(atop("Median", "n. maternal")))) + 
  facet_wrap(~species, nrow = 2) +
  theme_half_open() + 
  theme(axis.text.x = element_text(angle = 90)) + 
  labs(x = "Selectivity: Sample size", y = bquote(atop(italic(P)[Max],("Reproductive frequency")))) 
```
Figure S8. Median number of females in maternal condition in simulated data that were used to estimate maternity parameters subject to varying sample size, gear selectivity, reproductive frequency. 250 iterations were carried out for each simulation. 
\newpage

```{r, fig.width = 11, fig.height = 8.5}
filter(data, method_long %in% c("3PLF - estimated", par_name %in% "c")) %>% 
ggplot() + 
  geom_tile(aes(x = as.factor(Nsamples_sel), y = repro_freq, fill = n_immature)) + 
  geom_text(aes(x = as.factor(Nsamples_sel), y = repro_freq, label = round(n_immature, 0))) +
  scale_fill_viridis_c(trans = "log10") + 
  guides(fill = guide_colorbar(title = bquote(atop("Median", "n. immature")))) + 
  facet_wrap(~species, nrow = 2) +
  theme_half_open() + 
  theme(axis.text.x = element_text(angle = 90)) + 
  labs(x = "Selectivity: Sample size", y = bquote(atop(italic(P)[Max],("Reproductive frequency")))) 
```
Figure S9. Median number of immature females in simulated data that were used to estimate maternity parameters subject to varying sample size, gear selectivity, reproductive frequency. 250 iterations were carried out for each simulation. 
\newpage

```{r fig.width = 12, fig.height = 10}
ggplot(data %>% filter(par_name %in% "r_0")) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), rel_error, col = repro_freq, group = repro_freq)) +
  geom_line(aes(as.factor(Nsamples), rel_error, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  scale_color_brewer(palette = "Spectral") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) + 
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "Mean % relative error", title = "Bias - Reproductive Output") +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```

```{r fig.width = 12, fig.height = 10}
  ggplot(data %>% filter(par_name %in% "r_0")) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), abs_error, col = repro_freq, group = repro_freq)) +
  geom_line(aes(as.factor(Nsamples), abs_error, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  scale_color_brewer(palette = "Spectral") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) + 
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "Mean % relative absolute error", title = "Precision - Reproductive Output") +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```

>>>>

## Figures
```{r, fig.width = 12, fig.height = 10}
ggplot(data %>% filter(par_name %in% "m50")) +
  geom_point(aes(as.factor(Nsamples), conv_success, col = repro_freq, group = repro_freq)) + 
  geom_line(aes(as.factor(Nsamples), conv_success, col = repro_freq, group = repro_freq)) +
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) +
  scale_color_brewer(palette = "Spectral") + 
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Number of samples", y = "Convergence success (%)", title = "Model convergence") +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```
Figure S1. Convergance success of alternative logistic regression models fit (n = 300) for school shark and gummy shark.

```{r, fig.width = 12, fig.height = 10}
ggplot(data %>% filter(par_name %in% "m50")) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), rel_error, col = repro_freq, group = repro_freq)) +
  geom_line(aes(as.factor(Nsamples), rel_error, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  scale_color_brewer(palette = "Spectral") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) + 
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "Mean % relative error", title = expression("Bias - Length at 50% maternity")) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")

```
Figure S2. Bias (per cent relative error) in parameter estimates of $\hat{L'_{50}}$ using alternative logistic regression models. Each point reflects a mean value from 300 simulated data sets.

@@

```
Figure S3. Bias (per cent relative error) in parameter estimates of $\hat{P_{Max}}$ using alternative logistic regression models. Each point reflects a mean value from 300 simulated data sets. Note 2PLF-maturity and 3PLF-fixed methods both used pre-specified values for $P_{Max}$ and are identical.

```{r, fig.width = 12, fig.height = 10}
ggplot(data %>% filter(par_name %in% "m50")) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), abs_error, col = repro_freq, group = repro_freq)) +
  geom_line(aes(as.factor(Nsamples), abs_error, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  scale_color_brewer(palette = "Spectral") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) + 
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "Mean % absolute relative error", title = expression("Precision - Length at 50% maternity")) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```
Figure S4. Precision (per cent absolute error) in parameter estimates of $\hat{L'_{50}}$ using alternative logistic regression models. Each point reflects a mean value from 300 simulated data sets.

```{r, fig.width = 12, fig.height = 10}
ggplot(data %>% filter(par_name %in% "c")) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), abs_error, col = repro_freq, group = repro_freq)) +
  geom_line(aes(as.factor(Nsamples), abs_error, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  scale_color_brewer(palette = "Spectral") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) + 
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "Mean % absolute relative error", title = expression("Precision - "~italic(P)[Max])) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```
Figure S5. Precision (per cent absolute error) in parameter estimates of $\hat{P_{Max}}$ using alternative logistic regression models. Each point reflects a mean value from 300 simulated data sets. Note 2PLF-maturity and 3PLF-fixed methods both used pre-specified values for $P_{Max}$ and are identical. 
\newpage

```{r fig.width = 12, fig.height=7}
ggplot(data %>% filter(par_name %in% "m50", method_long %in% c("3PLF - estimated", "3PLF - fixed"))) +
  geom_hline(yintercept = 50, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), int_coverage, col = repro_freq, group = repro_freq)) +
  geom_line(aes(as.factor(Nsamples), int_coverage, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  scale_color_brewer(palette = "Spectral") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) + 
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "% interval coverage", title = expression("Interval coverage - Length at 50% maternity")) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```
Figure S6. Confidence interval coverage for $L'_{50}$ for 3PLF methods. Figure shows the percentage of simulations (n = 300) where the true parameter value fell within the 50% bootstrap confidence interval. 
\newpage

```{r fig.width = 12, fig.height=5}
ggplot(data %>% filter(par_name %in% "c", method_long %in% c("3PLF - estimated"))) +
  geom_hline(yintercept = 50, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), int_coverage, col = repro_freq, group = repro_freq)) +
  geom_line(aes(as.factor(Nsamples), int_coverage, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  scale_color_brewer(palette = "Spectral") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) + 
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "% interval coverage", title = expression("Interval coverage - "~italic(P)[Max])) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```
Figure S7. Confidence interval coverage for $P_{Max}$ for the 3PLF-estimated method. Figure shows the percentage of simulations (n = 300) where the true parameter value fell within the 50% bootstrap confidence interval. 
\newpage

```{r, fig.width = 11, fig.height = 8.5}
filter(data, method_long %in% c("3PLF - estimated", par_name %in% "c")) %>% 
  ggplot() + 
  geom_tile(aes(x = as.factor(Nsamples_sel), y = repro_freq, fill = n_maternal)) + 
  geom_text(aes(x = as.factor(Nsamples_sel), y = repro_freq, label = round(n_maternal, 0))) +
  scale_fill_viridis_c(trans = "log10") + 
  guides(fill = guide_colorbar(title = bquote(atop("Median", "n. maternal")))) + 
  facet_wrap(~species, nrow = 2) +
  theme_half_open() + 
  theme(axis.text.x = element_text(angle = 90)) + 
  labs(x = "Selectivity: Sample size", y = bquote(atop(italic(P)[Max],("Reproductive frequency")))) 
```
Figure S8. Median number of females in maternal condition in simulated data that were used to estimate maternity parameters subject to varying sample size, gear selectivity, reproductive frequency. 300 iterations were carried out for each simulation. 
\newpage

```{r, fig.width = 11, fig.height = 8.5}
filter(data, method_long %in% c("3PLF - estimated", par_name %in% "c")) %>% 
ggplot() + 
  geom_tile(aes(x = as.factor(Nsamples_sel), y = repro_freq, fill = n_immature)) + 
  geom_text(aes(x = as.factor(Nsamples_sel), y = repro_freq, label = round(n_immature, 0))) +
  scale_fill_viridis_c(trans = "log10") + 
  guides(fill = guide_colorbar(title = bquote(atop("Median", "n. immature")))) + 
  facet_wrap(~species, nrow = 2) +
  theme_half_open() + 
  theme(axis.text.x = element_text(angle = 90)) + 
  labs(x = "Selectivity: Sample size", y = bquote(atop(italic(P)[Max],("Reproductive frequency")))) 
```
Figure S9. Median number of immature females in simulated data that were used to estimate maternity parameters subject to varying sample size, gear selectivity, reproductive frequency. 300 iterations were carried out for each simulation. 
\newpage

```{r fig.width = 12, fig.height = 10}
ggplot(data %>% filter(par_name %in% "r_0")) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), rel_error, col = repro_freq, group = repro_freq)) +
  geom_line(aes(as.factor(Nsamples), rel_error, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  scale_color_brewer(palette = "Spectral") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) + 
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "Mean % relative error", title = "Bias - Reproductive Output") +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```
Figure S10. Bias (per cent relative error) in $R_{0}$ calculated using maternity parameters obtained from alternative logistic regression models. Each point reflects a mean value from 300 simulated data sets

```{r fig.width = 12, fig.height = 10}
  ggplot(data %>% filter(par_name %in% "r_0")) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), abs_error, col = repro_freq, group = repro_freq)) +
  geom_line(aes(as.factor(Nsamples), abs_error, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  scale_color_brewer(palette = "Spectral") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) + 
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "Mean % relative absolute error", title = "Precision - Reproductive Output") +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```
Figure S11. Precision (per cent absolute error) in $R_{0}$ calculated using maternity parameters obtained from alternative logistic regression models. Each point reflects a mean value from 300 simulated data sets
